R Notebook

### 2021-06-24 Exemples and Implementations.Rmd
Particle Filter aggiunto quello della Petrone

---
title: "R Notebook"
output:
  pdf_document: default
  html_notebook: default
---

@@

sim<-dlm.sim(n,sigma,tau,x0)
y<-sim$y
x<-sim$x

@@

@@

# COMPARISON (ANOTHER SECTION)
```{r}
library(ggpubr)
library(kableExtra)

@@

```{r}
truex<-x
estimatedx<-matrix(NA,ncol=6,nrow=6)
colnames(estimatedx)<-c("N","Threshold","KF","PF","APF","LWF")
estimatedx[,1]<-c(20,100,500,1000,1000,1000)
estimatedx[,2]<-c(0.5,0.5,0.5,0.5,0.25,0.1)
RMSE<-function(x,xhat){sqrt(mean((x - xhat)^2))}

@@

```{r echo=FALSE}
n=50
tau2=1
sigma2=1
sigma=sqrt(sigma2)
tau=sqrt(tau2)
x0=0

@@

@@

```{r echo=FALSE, fig.align='center', fig.cap="Kalman Filtered States with credible interval (in red)", fig.height=8, fig.pos='ht', fig.width=8, message=FALSE, warning=FALSE, results=F}
plot1<-Filtplot(dfsv,svpf,"Particle Filter")
plot2<-Filtplot(dfsv,svapf,"Auxiliary Particle Filter")
plot3<-Filtplot(dfsv,svlw,"Liu e West Filter")

ggarrange(plot1,plot2,plot3)
```

>>>>

---
title: "R Notebook"
output:
  pdf_document: default
  html_notebook: default
---
```{r include=FALSE}
library(ggplot2)
library(ggpubr)
library(kableExtra)
```

```{r include=FALSE}
#Calcolo intevalli di credibilità
#--------------------------------
CredInt<-function(fun){

  Filt<-Filtervalues(fun)
  mean<-Filt$mean
  sd<-Filt$sd
  vec<-NULL
  for(t in 1:length(mean)){
  if(mean[t]-1.96*sd[t]<truex[t] & truex[t]<mean[t]+1.96*sd[t]){vec[t]<-1}else{vec[t]<-0}
  }
  return(mean(vec))
}

#RMSE
#----
RMSE<-function(x,xhat){sqrt(mean((x - xhat)^2))}
```

@@

sim<-dlm.sim(n,sigma,tau,x0)
y<-sim$y
x<-sim$x
truex<-x

@@

\textbf{Particle Filter Petroni more efficient}
```{r}
PF2fun<-function(data,N,m0,C0,tau,sigma,r){
  if(missing(r)){r=2}else{}
  xs<-NULL
  ws<-NULL
  ess<-NULL
  x  = rnorm(N,m0,sqrt(C0))
  importancesd<-sqrt(tau - tau^2 /(tau + sigma))
  predsd <- sqrt(sigma+tau)
  w  = rep(1/N,N)

    means<-x+(tau/(tau+sigma))*(data[t]-x)
    x<-rnorm(N,means,importancesd)
    w1<-w*dnorm(data[t],x,predsd)

\textbf{comparison between Particle Filters}

```{r echo=FALSE}
pf1<-PFfun(y,1000,0,100,1,1)
pf2<-PF2fun(y,1000,0,100,1,1)
plotpf1<-Filtplot(df,pf1,"transition")
plotpf2<-Filtplot(df,pf2,"more efficient")

ggarrange(plotpf1,plotpf2)
```

```{r}
Comparethetwo<-matrix(NA,nrow=2,ncol=2)
colnames(Comparethetwo)<-c("Credible Interval","RMSE")
rownames(Comparethetwo)<-c("transition","more efficient")
Comparethetwo[1,1]<-CredInt(pf1)
Comparethetwo[2,1]<-CredInt(pf2)
Comparethetwo[1,2]<-RMSE(truex,Filtervalues(pf1)$mean)
Comparethetwo[2,2]<-RMSE(truex,Filtervalues(pf2)$mean)
```

```{r echo=FALSE}
kbl(Comparethetwo, align="c", longtable = T, booktabs = T, caption="Comparison",digits=3)
```

@@

# COMPARISON (ANOTHER SECTION)

```{r echo=FALSE, fig.align='center', fig.cap="Variances", fig.height=4, fig.pos='ht', fig.width=8, message=FALSE, warning=FALSE, results=F}

@@

```{r include=FALSE}
truex<-x
estimatedx<-matrix(NA,ncol=6,nrow=6)
colnames(estimatedx)<-c("N","Threshold","KF","PF","APF","LWF")
estimatedx[,1]<-c(20,100,500,1000,1000,1000)
estimatedx[,2]<-c(0.5,0.5,0.5,0.5,0.25,0.1)

@@

```{r echo=FALSE, fig.align='center', fig.cap="SV", fig.height=4, fig.pos='ht', fig.width=8, message=FALSE, warning=FALSE, results=F}
n=50
tau2=1
sigma2=1
sigma=sqrt(sigma2)
tau=sqrt(tau2)
x0=0

@@

#Plots (observetions in black and filtered states in red)
plot0<-ggplot(DLM.df,aes(x=timeframe))+
  geom_line(aes(y=y, col="Observations", linetype="Observations"))+
  geom_line(aes(y=x, col="True States", linetype="True States"))+
  geom_line(aes(y=m, col="Filtered States", linetype="Filtered States"))+
  geom_ribbon(aes(ymin = Low, ymax = Up),
              fill="red",alpha=0.16) +
    scale_color_manual("",
                      values=c("Observations" = "black",
                               "True States" = "black",
                               "Filtered States"= "red"))+
  scale_linetype_manual("",
                      values=c("Observations" = 1,
                               "True States" = 3,
                               "Filtered States"=1))+
    coord_cartesian(ylim=c(-6,6))+
  labs(x="Time",
       y="")+
  ggtitle("Kalman Filter")+
  theme_bw()+
    theme(legend.direction = "horizontal", legend.position = "bottom", legend.key = element_blank(), 
        legend.background = element_rect(fill = "white", colour = "gray30")) +
  theme(plot.title = element_text(hjust = 0.5))
```

@@

```{r echo=FALSE, fig.align='center', fig.cap="Comparison filter performances", fig.height=8, fig.pos='ht', fig.width=8, message=FALSE, warning=FALSE, results=F}
plot1<-Filtplot(dfsv,svpf,"Particle Filter")
plot2<-Filtplot(dfsv,svapf,"Auxiliary Particle Filter")
plot3<-Filtplot(dfsv,svlw,"Liu e West Filter")

ggarrange(plot0,plot1,plot2,plot3)
```
